\cvsection{Experience}
\begin{cventries}
    \cventry
        {Graduate Research Assistant}
        {University of Illinois at Chicago}
        {Chicago, IL}
        {May. 2016 - PRESENT}
        {
            \begin{cvitems}
                \item{Performed research to identify a predictive population estimation model using photos shared on social media under the collective advice of Prof. Tanya Berger-Wolf (UIC) and Emre Kiciman (Microsoft Research).}
                \item{ Mentored 3 undergraduate students from UIC in a project to infer if stripe-patterns in zebras are inherited.}
            \end{cvitems}
        }
    \cventry
        {Graduate Teaching Assistant}
        {University of Illinois at Chicago}
        {Chicago, IL}
        {Jan. 2016 - May. 2016}
        {
            \begin{cvitems}
                \item{Assisted Prof. Douglas Hogan for Introduction to Computing and Programming(C++) course in the CS department.}
            \end{cvitems}
        }
        
    \cventry
        {Technology Analyst}
        {J.P.Morgan Chase \& Co.}
        {Mumbai, India}
        {July. 2013 - July. 2015}
        {
            \begin{cvitems}
                \item {Built high performance real-time data-warehousing solutions using Abinitio in conjunction with Bash scripting.}
                \item{Pioneered in remodeling a load strategy that conserved over 2000 CPU and 100 human hours per month.}
                \item{Awarded the title of Subject Matter Expert for enabling the team to achieve tight service level agreements by formulating solutions that required a deep understanding of both functional and technical aspects of the project.}
            \end{cvitems}
        }
\end{cventries}
