\cvsection{Projects \& Thesis}
\begin{cventries}

\cventry
    {github.com/smenon8/AnimalWildlifeEstimator} % Job title
    {Animal Wildlife Estimator using Social Media} % Organization
    {Python3, R, Folium, sklearn, skimage, PyMongo, urllib2, plot.ly} % Location
    {Oct. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formulated a population estimation model for endangered animals using pictures mined from various social media platforms.}
        \item {Implemented and evaluated metrics for different machine learning algorithms in Python3 to predict the likelihood of an image being shared on social media based on various image, ecological as well biological features.}
        \item{Implemented middleware in Python to scrape wildlife images from Flickr, EXIF and beauty features of the scraped images were extracted using libraries implemented in R.}
        \item{nterpreted and quantified different levels of self-reporting or behavioral bias, location bias that are introduced in social networks while sharing wildlife pictures.}
      \end{cvitems}
    } 
\cventry
    {github.com/smenon8/SFParkResourceSearchSim} % Job title
    {SF Park Assist Simulator} % Organization
    {Python3, Google Maps API} % Location
    {Jan. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered real-time algorithms for searching available parking spots in San Francisco bay area using Python that adapt to both deterministic and probabilistic environments.}
        \item {Boosted the worst-case performance of the algorithms by 34\% compared to baseline algorithms.}
      \end{cvitems}
    }
\cventry
    {github.com/smenon8/TwitterSentimentsClassification} % Job title
    {Twitter Sentiment Classification} % Organization
    {Python3, sklearn, nltk, matplotlib} % Location
    {Aug. 2016 - Nov.2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and engineered different learning techniques for classifying sentiments for a Twitter dataset.}
        \item {Built various multi-class text classifiers that delivered promising F-scores and very high precision-recall metrics.}
      \end{cvitems}
    }


\end{cventries}
